A template for the \emph{arxiv} style

### 2021-08-18 main/main.Rmd
more content in framework and examples

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.path = "figures/")
library(cubble)
```

@@

Spatio-temporal data record changes of variables [for a reasonable length of period and spread across geographical region]. In this article, we consider spatio-temporal vector data, which are recorded in a fixed interval and are point based, characterised by longitude and latitude, in the spatial aspect. Examples of this type of data include the house price of a city or county, climate measures from weather stations in a country, and river level data from electronic gauges.

@@

In spatio-temporal data, a variable is usually either group-related or time-related. While time-related variables record variables that change in time, group-related variables are invariant to the time and have only one value per group. A cubble simplifies the workflow in spatio-temporal data through managing group and time-related variables separately in two forms: list-column and long form. The list column form:

@@

@@

Below are the how the list-column and long form look like for Australia climate data, which records daily precipitation, maximum and minimum temperature for 55 stations across Australia from 2015- 2020.

@@

```{r echo = FALSE}
climate_small %>% zoom()
```

# Manipulation and visualisation with `cubble`

@@

>>>>

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, 
                      fig.path = "figures/",
                      out.width = "100%", 
                      out.height = "30%")
```

```{r echo = FALSE}
library(cubble)
library(dplyr)
library(lubridate)
```

@@

Spatio-temporal data record changes of variables in spatially separated regions across time. In this article, we consider spatio-temporal vector data, which are recorded in a fixed interval and are point based, characterised by longitude and latitude, in the spatial aspect. Examples of this type of data include the house price of a city or county, climate measures from weather stations in a country, and river level data from electronic gauges.

@@

Spatio-temporal data can be thought of as characterised by three dimensions: group, time, and variable, which allows us to use a cube to represent the data. While group and time are can be seen as identifiers of the record, variables can be further divided into those that are group-related and time-related. Group-related variables are invariant to the time and have only one value per group while time-related variables change in time and requires both group and time to identify a record. Hence the cubic representation can be further simplified for those group-related variables as in the sketch \ref{fig:framework}, where group-related variables are squashed in the time dimension.

```{r framework, echo = FALSE, fig.cap = "Cubic representation of spatio-temporal data. (1) shows the full cube, (2) simplifies teh cube by squashing the time dimension of time-invariant variables. With (2), a slice along the group dimension will affect both time-variant and invariant variables as in (3) while, a slice along the time will only affect the tim-variant variables as in (4)."}
knitr::include_graphics(here::here("figures/cubble-framework-hand.jpeg"))
```

A cubble simplifies the workflow in spatio-temporal data through managing group and time-related variables separately in two forms: list-column and long form. The nested form:

@@

This form focuses on the time-invariant variable by squashing the time dimension

@@

Below are the how the nested and long form look like for Australia climate data, which records daily precipitation, maximum and minimum temperature for 55 stations across Australia from 2015- 2020. Notice that each station forms a group in both forms and specifically, the nested  and long form have a underlying `rowwise_df` and `grouped_df` respectively.

@@

```{r echo = FALSE}
climate_small %>% stretch()
```

With a cubic framework on mind, different types of manipulation with cubble can be thought of as slicing the cube in various way. The table below shows how some `dplyr` verbs are mapped into the operation in a cubble. With the existing grouping on the station, additional groupping can be added with `group_by` and removed with `ungrouped`. [talk about why it is useful]

```{r verbs, echo = FALSE, out.height = "50%", out.width = "100%", fig.cap = "sdfsdf"}
knitr::include_graphics(here::here("figures/cubble-verbs.png"))
```

@@

### Mutate and filter

In the first example, we want to only keep the stations that have `tmax` recorded in 2020. This requires first narrow down the records to those in 2020, determine if `tmax` is missing for each station, and then retain those stations that have `tmax` recorded. The year filtering is an operation on the time axis, so we start with the long form. Whether each station has `tmax` recorded is a result of each station, rather than of each time point, hence we need to switch to the nested form with `tamp()`. To calculate whether `tmax` is recorded, we mutate a column `tmax_missing` that takes `TRUE` if all the `tmax` in the nested list column `ts` are `NA` and `FALSE` otherwise. To get the stations that we want, we need another filter on `tmax_missing`.

```{r}
climate_small %>% 
  stretch() %>% 
  filter(year(date) == 2020) %>% 
  tamp() %>% 
  mutate(tmax_missing = ifelse(all(is.na(ts$tmax)), TRUE, FALSE)) %>% 
  filter(!tmax_missing)
```

### Join

Now we want to select the stations that have been registered with world meteorological organisation (WMO) and the dataset `station` has a column `wmo_id` that records this information. To do this task, we first need to join the `station` dataset with our climate dataset and then filter out those stations that don't have the WMO id. Since the join is by station rather than by time, we start with the nested form and write the exact same syntax of join and filter as with tidyverse.

```{r}
# join wmo_id for each station
to_join <- station %>% select(id, wmo_id)
out <- climate_small %>% 
  left_join(to_join, by = c("station" = "id")) %>% 
  filter(!is.na(wmo_id))
out
```

Sometimes, we would like to have station-wise and time-wise variables in the same form (i.e. when plotting glyph maps). This can also be seen as a joining task, on the long form, with the dataset to join being the metadata. `migrate()` is a verb introduced as the shortcut for `left_join()` with a cubble's metadata and below is the comparison of the two syntaxes.

```{r}
out %>% 
  stretch() %>% 
  migrate(station, lat, long)
```

### 2021-08-18 main/main.tex
more content in framework and examples

@@

Spatio-temporal data record changes of variables {[}for a reasonable
length of period and spread across geographical region{]}. In this
article, we consider spatio-temporal vector data, which are recorded in
a fixed interval and are point based, characterised by longitude and
latitude, in the spatial aspect. Examples of this type of data include
the house price of a city or county, climate measures from weather
stations in a country, and river level data from electronic gauges.

@@

In spatio-temporal data, a variable is usually either group-related or
time-related. While time-related variables record variables that change
in time, group-related variables are invariant to the time and have only
one value per group. A cubble simplifies the workflow in spatio-temporal
data through managing group and time-related variables separately in two
forms: list-column and long form. The list column form:

@@

Below are the how the list-column and long form look like for Australia
climate data, which records daily precipitation, maximum and minimum
temperature for 55 stations across Australia from 2015- 2020.

\begin{verbatim}
## # Cubble: station-wise: list-column
## # Group:  station [55]
## # Meta:   station [fct], lat [dbl], long [dbl], elevation [dbl], name [fct]
##    station       lat  long elevation name                ts                  
##    <fct>       <dbl> <dbl>     <dbl> <fct>               <list>              
##  1 ASN00001019 -14.3  127.      23   kalumburu           <tbl_ts [2,147 x 4]>
##  2 ASN00002012 -18.2  128.     422   halls creek airport <tbl_ts [2,191 x 4]>
##  3 ASN00003003 -17.9  122.       7.4 broome airport      <tbl_ts [2,192 x 4]>
##  4 ASN00006011 -24.9  114.       4   carnarvon airport   <tbl_ts [2,192 x 4]>
##  5 ASN00009021 -31.9  116.      15.4 perth airport       <tbl_ts [2,192 x 4]>
##  6 ASN00009193 -32.0  116.      43.1 rottnest island     <tbl_ts [2,192 x 4]>
##  7 ASN00009518 -34.4  115.      13   cape leeuwin        <tbl_ts [2,184 x 4]>
##  8 ASN00009789 -33.8  122.      25   esperance           <tbl_ts [2,187 x 4]>
##  9 ASN00010286 -31.6  117.     217.  cunderdin airfield  <tbl_ts [2,190 x 4]>
## 10 ASN00010917 -32.7  117.     275   wandering           <tbl_ts [2,192 x 4]>
## # ... with 45 more rows
\end{verbatim}

\begin{verbatim}
## # Cubble: time-wise: long form [tsibble]
## # Group:  station [55]
## # Meta:   station [fct], lat [dbl], long [dbl], elevation [dbl], name [fct]
##    station     date        prcp  tmax  tmin
##    <fct>       <date>     <dbl> <dbl> <dbl>
##  1 ASN00001019 2015-01-01   164  31.5  25  
##  2 ASN00001019 2015-01-02   124  31.3  25  
##  3 ASN00001019 2015-01-03    50  29.2  24.7
##  4 ASN00001019 2015-01-04   204  32.1  24.3
##  5 ASN00001019 2015-01-05   412  31.4  24.6
##  6 ASN00001019 2015-01-06   200  28.7  25.1
##  7 ASN00001019 2015-01-07   822  30.2  24.5
##  8 ASN00001019 2015-01-08    22  31    26.6
##  9 ASN00001019 2015-01-09    62  32.7  26.2
## 10 ASN00001019 2015-01-10   274  32.9  22.6
## # ... with 120,311 more rows
\end{verbatim}

\hypertarget{manipulation-and-visualisation-with-cubble}{%
\section{\texorpdfstring{Manipulation and visualisation with
\texttt{cubble}}{Manipulation and visualisation with cubble}}\label{manipulation-and-visualisation-with-cubble}}

@@

>>>>

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}

@@

Spatio-temporal data record changes of variables in spatially separated
regions across time. In this article, we consider spatio-temporal vector
data, which are recorded in a fixed interval and are point based,
characterised by longitude and latitude, in the spatial aspect. Examples
of this type of data include the house price of a city or county,
climate measures from weather stations in a country, and river level
data from electronic gauges.

@@

Spatio-temporal data can be thought of as characterised by three
dimensions: group, time, and variable, which allows us to use a cube to
represent the data. While group and time are can be seen as identifiers
of the record, variables can be further divided into those that are
group-related and time-related. Group-related variables are invariant to
the time and have only one value per group while time-related variables
change in time and requires both group and time to identify a record.
Hence the cubic representation can be further simplified for those
group-related variables as in the sketch \ref{fig:framework}, where
group-related variables are squashed in the time dimension.

\begin{figure}
\includegraphics[width=1\linewidth,height=0.3\textheight]{/Users/hzha400/Documents/PhD/research/paper-cubble/figures/cubble-framework-hand} \caption{Cubic representation of spatio-temporal data. (1) shows the full cube, (2) simplifies teh cube by squashing the time dimension of time-invariant variables. With (2), a slice along the group dimension will affect both time-variant and invariant variables as in (3) while, a slice along the time will only affect the tim-variant variables as in (4).}\label{fig:framework}
\end{figure}

A cubble simplifies the workflow in spatio-temporal data through
managing group and time-related variables separately in two forms:
list-column and long form. The nested form:

@@

Below are the how the nested and long form look like for Australia
climate data, which records daily precipitation, maximum and minimum
temperature for 55 stations across Australia from 2015- 2020. Notice
that each station forms a group in both forms and specifically, the
nested and long form have a underlying \texttt{rowwise\_df} and
\texttt{grouped\_df} respectively.

\begin{verbatim}
## # Cubble: station-wise: nested form
## # Group:  station [55]
##    station       lat  long elevation name                ts                  
##    <fct>       <dbl> <dbl>     <dbl> <fct>               <list>              
##  1 ASN00001019 -14.3  127.      23   kalumburu           <tbl_ts [2,147 x 4]>
##  2 ASN00002012 -18.2  128.     422   halls creek airport <tbl_ts [2,191 x 4]>
##  3 ASN00003003 -17.9  122.       7.4 broome airport      <tbl_ts [2,192 x 4]>
##  4 ASN00006011 -24.9  114.       4   carnarvon airport   <tbl_ts [2,192 x 4]>
##  5 ASN00009021 -31.9  116.      15.4 perth airport       <tbl_ts [2,192 x 4]>
##  6 ASN00009193 -32.0  116.      43.1 rottnest island     <tbl_ts [2,192 x 4]>
##  7 ASN00009518 -34.4  115.      13   cape leeuwin        <tbl_ts [2,184 x 4]>
##  8 ASN00009789 -33.8  122.      25   esperance           <tbl_ts [2,187 x 4]>
##  9 ASN00010286 -31.6  117.     217.  cunderdin airfield  <tbl_ts [2,190 x 4]>
## 10 ASN00010917 -32.7  117.     275   wandering           <tbl_ts [2,192 x 4]>
## # ... with 45 more rows
\end{verbatim}

\begin{verbatim}
## # Cubble: time-wise: long form [tsibble]
## # Group:  station [55]
##    station     date        prcp  tmax  tmin
##    <fct>       <date>     <dbl> <dbl> <dbl>
##  1 ASN00001019 2015-01-01   164  31.5  25  
##  2 ASN00001019 2015-01-02   124  31.3  25  
##  3 ASN00001019 2015-01-03    50  29.2  24.7
##  4 ASN00001019 2015-01-04   204  32.1  24.3
##  5 ASN00001019 2015-01-05   412  31.4  24.6
##  6 ASN00001019 2015-01-06   200  28.7  25.1
##  7 ASN00001019 2015-01-07   822  30.2  24.5
##  8 ASN00001019 2015-01-08    22  31    26.6
##  9 ASN00001019 2015-01-09    62  32.7  26.2
## 10 ASN00001019 2015-01-10   274  32.9  22.6
## # ... with 120,311 more rows
\end{verbatim}

With a cubic framework on mind, different types of manipulation with
cubble can be thought of as slicing the cube in various way. The table
below shows how some \texttt{dplyr} verbs are mapped into the operation
in a cubble. With the existing grouping on the station, additional
groupping can be added with \texttt{group\_by} and removed with
\texttt{ungrouped}. {[}talk about why it is useful{]}

\begin{figure}
\includegraphics[width=1\linewidth,height=0.5\textheight]{/Users/hzha400/Documents/PhD/research/paper-cubble/figures/cubble-verbs} \caption{sdfsdf}\label{fig:verbs}
\end{figure}

@@

\hypertarget{mutate-and-filter}{%
\subsubsection{Mutate and filter}\label{mutate-and-filter}}

In the first example, we want to only keep the stations that have
\texttt{tmax} recorded in 2020. This requires first narrow down the
records to those in 2020, determine if \texttt{tmax} is missing for each
station, and then retain those stations that have \texttt{tmax}
recorded. The year filtering is an operation on the time axis, so we
start with the long form. Whether each station has \texttt{tmax}
recorded is a result of each station, rather than of each time point,
hence we need to switch to the nested form with \texttt{tamp()}. To
calculate whether \texttt{tmax} is recorded, we mutate a column
\texttt{tmax\_missing} that takes \texttt{TRUE} if all the \texttt{tmax}
in the nested list column \texttt{ts} are \texttt{NA} and \texttt{FALSE}
otherwise. To get the stations that we want, we need another filter on
\texttt{tmax\_missing}.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{climate\_small }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{stretch}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{filter}\NormalTok{(}\FunctionTok{year}\NormalTok{(date) }\SpecialCharTok{==} \DecValTok{2020}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{tamp}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{tmax\_missing =} \FunctionTok{ifelse}\NormalTok{(}\FunctionTok{all}\NormalTok{(}\FunctionTok{is.na}\NormalTok{(ts}\SpecialCharTok{$}\NormalTok{tmax)), }\ConstantTok{TRUE}\NormalTok{, }\ConstantTok{FALSE}\NormalTok{)) }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{filter}\NormalTok{(}\SpecialCharTok{!}\NormalTok{tmax\_missing)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # Cubble: station-wise: nested form
## # Group:  station [55]
##    station      lat  long elevation name             ts             tmax_missing
##    <fct>      <dbl> <dbl>     <dbl> <fct>            <list>         <lgl>       
##  1 ASN000010~ -14.3  127.      23   kalumburu        <tbl_ts [366 ~ FALSE       
##  2 ASN000020~ -18.2  128.     422   halls creek air~ <tbl_ts [366 ~ FALSE       
##  3 ASN000030~ -17.9  122.       7.4 broome airport   <tbl_ts [366 ~ FALSE       
##  4 ASN000060~ -24.9  114.       4   carnarvon airpo~ <tbl_ts [366 ~ FALSE       
##  5 ASN000090~ -31.9  116.      15.4 perth airport    <tbl_ts [366 ~ FALSE       
##  6 ASN000091~ -32.0  116.      43.1 rottnest island  <tbl_ts [366 ~ FALSE       
##  7 ASN000095~ -34.4  115.      13   cape leeuwin     <tbl_ts [366 ~ FALSE       
##  8 ASN000097~ -33.8  122.      25   esperance        <tbl_ts [361 ~ FALSE       
##  9 ASN000102~ -31.6  117.     217.  cunderdin airfi~ <tbl_ts [366 ~ FALSE       
## 10 ASN000109~ -32.7  117.     275   wandering        <tbl_ts [366 ~ FALSE       
## # ... with 45 more rows
\end{verbatim}

\hypertarget{join}{%
\subsubsection{Join}\label{join}}

Now we want to select the stations that have been registered with world
meteorological organisation (WMO) and the dataset \texttt{station} has a
column \texttt{wmo\_id} that records this information. To do this task,
we first need to join the \texttt{station} dataset with our climate
dataset and then filter out those stations that don't have the WMO id.
Since the join is by station rather than by time, we start with the
nested form and write the exact same syntax of join and filter as with
tidyverse.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# join wmo\_id for each station}
\NormalTok{to\_join }\OtherTok{\textless{}{-}}\NormalTok{ station }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{select}\NormalTok{(id, wmo\_id)}
\NormalTok{out }\OtherTok{\textless{}{-}}\NormalTok{ climate\_small }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{left\_join}\NormalTok{(to\_join, }\AttributeTok{by =} \FunctionTok{c}\NormalTok{(}\StringTok{"station"} \OtherTok{=} \StringTok{"id"}\NormalTok{)) }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{filter}\NormalTok{(}\SpecialCharTok{!}\FunctionTok{is.na}\NormalTok{(wmo\_id))}
\NormalTok{out}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # Cubble: station-wise: nested form
## # Group:  station [51]
##    station       lat  long elevation name              ts                 wmo_id
##    <fct>       <dbl> <dbl>     <dbl> <fct>             <list>              <dbl>
##  1 ASN00001019 -14.3  127.      23   kalumburu         <tbl_ts [2,147 x ~  94100
##  2 ASN00002012 -18.2  128.     422   halls creek airp~ <tbl_ts [2,191 x ~  94212
##  3 ASN00003003 -17.9  122.       7.4 broome airport    <tbl_ts [2,192 x ~  94203
##  4 ASN00006011 -24.9  114.       4   carnarvon airport <tbl_ts [2,192 x ~  94300
##  5 ASN00009021 -31.9  116.      15.4 perth airport     <tbl_ts [2,192 x ~  94610
##  6 ASN00009193 -32.0  116.      43.1 rottnest island   <tbl_ts [2,192 x ~  94602
##  7 ASN00009518 -34.4  115.      13   cape leeuwin      <tbl_ts [2,184 x ~  94601
##  8 ASN00009789 -33.8  122.      25   esperance         <tbl_ts [2,187 x ~  94638
##  9 ASN00010286 -31.6  117.     217.  cunderdin airfie~ <tbl_ts [2,190 x ~  95625
## 10 ASN00010917 -32.7  117.     275   wandering         <tbl_ts [2,192 x ~  95640
## # ... with 41 more rows
\end{verbatim}

Sometimes, we would like to have station-wise and time-wise variables in
the same form (i.e.~when plotting glyph maps). This can also be seen as
a joining task, on the long form, with the dataset to join being the
metadata. \texttt{migrate()} is a verb introduced as the shortcut for
\texttt{left\_join()} with a cubble's metadata and below is the
comparison of the two syntaxes.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{out }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{stretch}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{migrate}\NormalTok{(station, lat, long)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # Cubble: time-wise: long form
## # Group:  station [55]
##    station     date        prcp  tmax  tmin   lat  long
##    <fct>       <date>     <dbl> <dbl> <dbl> <dbl> <dbl>
##  1 ASN00001019 2015-01-01   164  31.5  25   -14.3  127.
##  2 ASN00001019 2015-01-02   124  31.3  25   -14.3  127.
##  3 ASN00001019 2015-01-03    50  29.2  24.7 -14.3  127.
##  4 ASN00001019 2015-01-04   204  32.1  24.3 -14.3  127.
##  5 ASN00001019 2015-01-05   412  31.4  24.6 -14.3  127.
##  6 ASN00001019 2015-01-06   200  28.7  25.1 -14.3  127.
##  7 ASN00001019 2015-01-07   822  30.2  24.5 -14.3  127.
##  8 ASN00001019 2015-01-08    22  31    26.6 -14.3  127.
##  9 ASN00001019 2015-01-09    62  32.7  26.2 -14.3  127.
## 10 ASN00001019 2015-01-10   274  32.9  22.6 -14.3  127.
## # ... with 111,562 more rows
\end{verbatim}
